\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}


\title{Supervision Agreement \\[0.5cm] \small Utilising Machine Learning in the Cement and Concrete Industry}
\author{Frederik Gantriis Møller \& Jaike Van Twiller}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

This supervision agreement sets out how we'll work together on the mandatory Research Project in the 3rd semester of the Computer Science Master's. The goal is to make sure both student and supervisor have the same expectations for meetings, feedback, timeline, and communication.

\section{Project Timeline}

The project will run in three stages:
\begin{enumerate}
    \item Define the project scope (start of September)
    \item Collaborate with the company and build most of the code (mid September to mid November)
    \item Finalize the product and complete the academic report (end of November to mid December)
\end{enumerate}
This plan may change if the company’s needs shift.

\section{Meetings}

We'll meet every Friday at 13:00 for 30 minutes. Meetings can be extended or cancelled depending on what’s needed and everyone’s availability.

\section{Feedback}

Feedback will be direct and honest, so expectations are clear. The student should clearly communicate what kind of feedback is needed from the supervisor.

\section{Communication}

Most communication will happen in our weekly meetings. If something urgent comes up, we’ll use email or Microsoft Teams.

\vspace{2cm}
\noindent
\begin{tabular}{p{0.4\textwidth} p{0.1\textwidth} p{0.4\textwidth}}
    \textbf{Student} & & \textbf{Supervisor} \\[1.5cm]
    \hrulefill & & \hrulefill \\
    Date: \hrulefill & & Date: \hrulefill \\
\end{tabular}

\end{document}
