
\section{Data Analysis}

This project uses data given by \ap. All data is collected from the preheater tower mentioned in \autoref{sec:introduction}. This includes the following datapoints:

\begin{itemize}
    \item Feed to Oven (tons per day)
    \item Top Pressure (mBar)
    \item Top Temperature (Degrees)
    \item Bottom Pressure (mBar)
    \item Bottom Temperature (Degrees)
    \item First Step Bottom Temperature (Degrees)
    \item Second Step Bottom Temperature (Degrees)
    \item Second Step Top Temperature (Degrees)
    \item Flue Gas Fan (Power)
    \item Flue Gas Fan (Current)
\end{itemize}

All of these data-points are then 

\section{Descriptive Statistics}

\todo{Include a section with all the descriptive statistics from all different features}

\todo{Include section concerning Pearson and Spearman correlation, both overall and for each step}

\subsection{Pre-processing and Feature Engineering}

\todo{Explain the steps of simpleimputer and so on}

\subsection{Train-Validation-Test Splitting Strategy}

In regards to splitting the dataset into a train, validation and test dataset, the main focus has been to keep the order of the data throughout all processing. The reason being, that time-series data may include patterns present over a given time-period that models are able to learn. Therefore, the initial splitting only concerned splitting the dataset into train and test. The size of the training dataset was determined using try-and-test experimentation to choose an optimal size.

Afterwards, the training dataset are split into different folds to enable cross-validation. The data is split using \textit{TimeSeriesSplit} \footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.model_selection.TimeSeriesSplit.html}}. The method splits the data into equal portions, before being trained on the model using cross-validation. The reason for using the \textit{TimeSeriesSplit}, is to ensure that the data isn't shuffled, since all entries in a given split to be a continuous sequence. This ensures that the model can use patterns over a given time-period to predict future outcomes.

\subsection{Specific transformations}